\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{inter}
\renewcommand*\familydefault{\sfdefault}

\usepackage{geometry}
\geometry{a4paper, top=1.8cm, bottom=1in, left=2.5cm, right=2.5cm}

\setcounter{secnumdepth}{0} % remove section numbering
\pdfgentounicode=1 % make ATS friendly

\usepackage{enumitem}
\setlist[itemize]{noitemsep, left=2em}
\setlist[description]{itemsep=0pt}
\setlist[enumerate]{align=left}
\usepackage[dvipsnames]{xcolor}
\colorlet{icnclr}{gray}
\usepackage{titlesec}
\titlespacing{\subsection}{0pt}{*0}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}
\titleformat{\section}{\color{Sepia}\large\fontseries{black}\selectfont\uppercase}{}{}{\ruleafter}[\global\RemVStrue]
\titleformat{\subsection}{\fontseries{bold}\selectfont}{}{}{\rvs}
\titleformat{\subsubsection}{\color{gray}\fontseries{bold}\selectfont}{}{}{}

\usepackage{xhfill}
\newcommand\ruleafter[1]{#1~\xrfill[.5ex]{1pt}[gray]} % add rule after title in .5 x-height

\newif\ifRemVS % remove vspace between \section & \subsection
\newcommand{\rvs}{
    \ifRemVS
        \vspace{-1.5ex}
    \fi
    \global\RemVSfalse
}

\usepackage{fontawesome5}
\usepackage[bookmarks=false]{hyperref} % [imp!]
\hypersetup{
    colorlinks=true,
    urlcolor=Sepia,
    pdftitle={My Resume}
}

\usepackage[page]{totalcount}
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}

\usepackage{amsmath}
\usepackage{amsfonts}

\begin{document}

\begin{center}
    {\fontsize{28}{28}\selectfont Ahamed Dhahlan} \\ \bigskip

    {\color{icnclr}\faPhone} (+94) 77 958 09 67 \quad
    {\color{icnclr}\faEnvelope} \href{mailto:peahameddhahlan3890@gmail.com}{peahameddhahlan3890@gmail.com} \quad
    {\color{icnclr}\faLinkedin} \href{https://www.linkedin.com/[YOUR_LINKEDIN_PROFILE_URL]}{LinkedIn} \quad
    {\color{icnclr}\faGithub} \href{https://github.com/[YOUR_GITHUB_USERNAME]}{Github}
\end{center}

\section{Summary}
Experienced data scientist and machine learning engineer with a strong focus on transformers and LangChain agentic models. Skilled in developing and deploying advanced natural language processing (NLP) solutions, leveraging frameworks like PyTorch, Hugging Face Transformers, and LangChain to create intelligent, context-aware systems. Proficient in Python, R, and SQL, with hands-on experience in building end-to-end machine learning pipelines, predictive modeling, and data-driven decision-making. Adept at delivering scalable solutions that drive innovation and enhance user engagement.

\section{Experience}
\subsection{Software Engineer Intern \hfill Sep \textendash{} Present 2024}
\subsubsection{Paralegal.lk, Colombo, Sri Lanka} 
\begin{itemize}
    \item Integrated payment solutions into the website using PayHere services and React, enhancing transaction capabilities.
    \item Conducted network analysis of legal case citations, significantly improving the website’s search engine efficiency by 200\%.
    \item Collaborated on diverse web development tasks, emphasizing front-end functionality and optimizing user experience.
\end{itemize}
\subsection{Electrical and Information Engineer Intern \hfill August \textendash{} January 2023\textendash{}2024}
\subsubsection{Mahaweli Authority of Sri Lanka, Victoria, Sri Lanka}
\begin{itemize}
    \item Led the design and implementation of a cutting-edge real-time dam simulation system for the Victoria Dam Control Room and Observation Platform.
    \item Implemented a Dam Gate opening prediction app.
\end{itemize}

\section{Projects}
\subsection{Singlish GPT: Language Model for Sinhala in English Letters}
\begin{itemize}
    \item Developed a GPT model for Singlish text processing and generation using mT5, achieving 92\% accuracy in text generation.
    \item \textbf{Technology Used:} Python, Hugging Face Transformers, PyTorch, Aksharamukha, Google Cloud
\end{itemize}
\subsection{DeChatIn: AI-Powered Chatbot for Conversational and Voice Interactions}
\begin{itemize}
    \item Developed an AI-driven chatbot with voice conversation capabilities, enabling natural interactions and seamless speech mode switching.
    \item Enhanced conversational dynamics with real-time speech synthesis, improving user engagement.
    \item \textbf{Technology Used:} Python, Streamlit, Google Gemma, Hugging Face Transformers, Google Text-to-Speech (TTS), NLP, Generative AI
\end{itemize}
\subsection{CodeForgeAI: Code Generation from Webpage Screenshots}
\begin{itemize}
    \item Created a tool to generate code from webpage screenshots with real-time previews, enhancing coding efficiency.
    \item \textbf{Technology Used:} Python, Django, React, Gemini, Generative AI
\end{itemize}
\subsection{EduZone: An Innovative E-learning Platform \textendash{} Group Project}
\begin{itemize}
    \item Developed a comprehensive e-learning platform with courses and projects, using React (frontend) and Django (backend).
    \item Used Python and Django for server-side logic and database management.
    \item \textbf{Technology Used:} React, Python, Django, JWT, Machine Learning
\end{itemize}
\subsection{Trading Helper Agent: A Conversational Assistant for Stock Analysis}
\begin{itemize}
    \item Built an intelligent conversational agent for stock analysis, integrating tools for fetching stock data, news, and calculating moving averages.
    \item Used LangChain for seamless interaction with external tools and a custom Google Gemma language model.
    \item Implemented dynamic query handling and real-time processing.
    \item \textbf{Technology Used:} Python, Hugging Face Transformers, LangChain Agent, PyTorch, Streamlit, YFinance
\end{itemize}
\subsection{Third Eye Glove for the Visually Impaired}
\begin{itemize}
    \item Developed a wearable glove using computer vision and ultrasonic sensors to detect obstacles and provide real-time feedback.
    \item Implemented advanced image processing techniques for object and terrain identification.
    \item \textbf{Technology Used:} Raspberry Pi, ATmega328p, Computer Vision, Image Processing, Ultrasonic Sensors, Python, OpenCV
\end{itemize}

\section{Education}
\subsection{Bachelor of Science in Engineering (Honors) \textendash{} Electrical and Information \hfill 2021 \textendash{} 2025}
\subsubsection{University of Ruhuna, Galle, Sri Lanka}
\subsection{GCE Advanced Level and GCE Ordinary Level \hfill 2017 \textendash{} 2019}
\subsubsection{Zahira College, Kalmunai, Sri Lanka}

\section{Skills}
\subsection{Programming Languages}
\begin{itemize}
    \item C, C++, Python, JavaScript
\end{itemize}
\subsection{Data Science/ML Libraries}
\begin{itemize}
    \item TensorFlow, PyTorch, scikit-learn, NumPy, Pandas
\end{itemize}
\subsection{Machine Learning Skills}
\begin{itemize}
    \item NLP, Computer Vision, Model Training, Hyperparameter Tuning
\end{itemize}
\subsection{Web Development}
\begin{itemize}
    \item HTML, CSS, JavaScript, React.js, Node.js, Django
\end{itemize}
\subsection{Databases}
\begin{itemize}
    \item MySQL, MongoDB
\end{itemize}
\subsection{Development Tools}
\begin{itemize}
    \item Git, VSCode, Jupyter Notebook
\end{itemize}
\subsection{Soft Skills}
\begin{itemize}
    \item Problem Solving, Self-Learning, Presentation, Adaptability, Critical Thinking
\end{itemize}

\section{Certificates}
\begin{itemize}
    \item Introduction to Web Development with HTML, CSS, JavaScript
    \item Introduction to Cloud Computing
    \item Introduction to Deep Learning \& Neural Networks with Keras
    \item Machine Learning with Python
    \item Python for Data Analysis: Pandas \& NumPy
    \item edX Verified Certificate for Data Science: Machine Learning
    \item SystemVerilog for ASIC/FPGA Design \& Simulation
\end{itemize}

\section{Achievements}
\begin{itemize}
    \item Participant, Commercial Bank Hackathon, June 2024
    \item 2nd Runners up, Haxtreme 2.0, IEEE Society, November 2023
    \item Top 10\%, AWS Deep Racer, August 2023
\end{itemize}

\section{References}
References available upon request.

\end{document}